---
title: "p8105_hw4_sw3236"
author: "Shuang WU"
date: "October 25, 2017"
output: html_document
---

The project leader for this problem is Shuang Wu, and the collabrator is Dong Yuan.

#Problem1

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
```

This problem uses the pups dataset. The original data file includes data in ¡°wide¡± format: the post-natal days on which developmental landmarks are reached are stored in columns called PD_outcome. The project lead will convert these data to ¡°long¡± format.
```{r}
pups <- read_csv(file = "./data/FAS_pups.csv", col_types = "ciiiii")
pups <- 
  pups %>%
  clean_names() %>%
  gather(key = pd_outcome, value = days, pd_ears:pd_walk)
```

The collaborator will create a plot showing the distribution of post-natal days for each developmental landmark.

```{r density,warning=FALSE}
pup_distri = 
  pups %>% 
    ggplot(aes(x = days,y = ..density..,color = pd_outcome)) +
      geom_density(aes(fill = pd_outcome),alpha = 0.2) +
         labs(title = "Distribution of post-natal days")
pup_distri
```

From the plot we can see that the distribution of post-natal days differ between landmarks. The density of ears and eyes are higher, while pivot and walk and relatively spread. The eyes have the most longer post_natal days and ears are the first coming after birth.

